Modeling the Linux page cache for accurate simulation of data-intensive applications

### 2020-12-14 paper_io_sim.tex
more in conclusion

    Page cache simulation would be instrumental in a number of studies.
    For instance, it is now common for HPC clusters to run 
    application jobs in Linux control groups (cgroups), where resource consumption 
    including memory is controlled.

    With the page cache, I/O times are strongly dependent on the amount of
    available memory, which is itself impacted by the use of anonymous
    memory by applications. A more accurate simulation of application
    memory consumption would therefore be a relevant future direction to
    further improve I/O simulation.

    I/Os remain much more complex than is currently available in simulation
    models.

        Simulation results could be made even more accurate by a deeper
        investigation of page cache flushing and eviction order. 
        The availability of asymmetrical bandwidths in the
        forthcoming \simgrid release will also directly improve our
        simulation accuracy.

        Relevant future work includes simulating
        application memory consumption, random I/O, file readahead and
        persistent disk storage.

        \tristan{discussion could be fleshed out. cgroups}

>>>>

    Page cache simulation would be instrumental in a number of studies. For
    instance, it is now common for HPC clusters to run application jobs in
    Linux control groups (cgroups), where resource consumption, including
    memory and therefore page cache usage, is limited. Using our simulator,
    it would be possible to model the interaction between memory allocation
    and I/O performance, with the goal to improve scheduling algorithms.
    Our simulator could also be utilized to evaluate solutions that
    reduce the impact of network file transfers on distributed
    applications, such as burst
    buffers~\cite{ferreiradasilva-fgcs-bb-2019}, hierarchical file
    systems~\cite{islam2015triple}, active storage, or specific
    hardware architectures~\cite{hayot2020performance}.

    However, I/Os remain much more complex than is currently available in
    simulation models, which could drastically limit their accuracy. A more
    accurate description of the use of anonymous memory by applications
    would be an important extension directly related to our page
    cache model. With the page cache indeed, I/O times are indeed strongly
    dependent on the amount of available memory, which is itself impacted
    by the use of anonymous memory by applications. File access patterns, 
    including random I/O, might also be worth describing, as they directly impact the content of the page cache.

        % Simulation results could be made even more accurate by a deeper
        % investigation of page cache flushing and eviction order. 
        % The availability of asymmetrical bandwidths in the
        % forthcoming \simgrid release will also directly improve our
        % simulation accuracy.

        % Relevant future work includes simulating
        % application memory consumption, random I/O, file readahead and
        % persistent disk storage.

        % \tristan{discussion could be fleshed out. cgroups}
